CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

@@

```{r testing}
# Hypothesis testing         
df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA)#, BPPARAM=SnowParam(18)) 
```

## Discovery cohort
```{r plot.discovery}
# plot discovery and testing.      
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed") 
```

@@

	plot_module( mod, df_test, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt", 5)   
	})

@@

## Replication cohort
```{r second.cohort, fig.width=8, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

	plot_module( mod, df_test, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})

@@

@@

```{r testing.Dx}
# Hypothesis testing     
df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA)  
```

## Discovery cohort
```{r plot.discovery.Dx}
# plot discovery and testing.  
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

	plot_module( mod, df_test, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
	})

@@

## Replication cohort
```{r second.cohort.Dx, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

	plot_module( mod, df_test, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})

@@

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})

>>>>

diff.net.Sex = get_difference_network(resid.add[[resVersion]], METADATA, variable)

# Discover clusters in first cohort
#----------------------------------
C.diff.discovery = diff.net.Sex[[1]][keep.ensID,keep.ensID]

@@

dynamicColors.Sex = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors.Sex)
hist(tab, xlab="Cluster size")
```

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA)#, BPPARAM=SnowParam(18)) 
```

## Discovery cohort
```{r plot.discovery}
# plot discovery and testing.      
ggplot(df_test.Sex, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed") 
```

@@

figList = lapply(df_test.Sex$Module[1:5], function(mod){

	plot_module( mod, df_test.Sex, METADATA, dynamicColors.Sex, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt", 5)   
	})

@@

## Replication cohort
```{r second.cohort, fig.width=8, fig.height=12}
df_cohort2 = df_test.Sex[df_test.Sex$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

	plot_module( mod, df_test.Sex, METADATA, dynamicColors.Sex, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})

@@

diff.net.Dx = get_difference_network(resid.add[[resVersion]], METADATA, variable)

# Discover clusters in first cohort
#----------------------------------
C.diff.discovery = diff.net.Dx[[1]][keep.ensID,keep.ensID]

@@

dynamicColors.Dx = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors)
hist(tab, xlab="Cluster size")
```

```{r testing.Dx}
# Hypothesis testing     
df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA)  
```

## Discovery cohort
```{r plot.discovery.Dx}
# plot discovery and testing.  
ggplot(df_test.Dx, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

	plot_module( mod, df_test.Dx, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
	})

@@

## Replication cohort
```{r second.cohort.Dx, fig.width=6, fig.height=12}
df_cohort2 = df_test.Dx[df_test.Dx$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

	plot_module( mod, df_test.Dx, METADATA, dynamicColors.Dx, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})

@@

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC", lvlidx=1:2)

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC", lvlidx=3:4)

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC", lvlidx=1:4) 
	})
